The \project{unRAVE} catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2016-09-09 article/unrave.tex
update author list and affiliations, etc

%% This file is part of the UNRAVE Project 
%% Copyright 2016 the authors.  All rights reserved.

%% TODO:
%% Co-authors: Look for \stub{}s. If you can expand it, do so!

\documentclass[preprint,trackchanges]{aastex}

@@

%\usepackage{xcolor}
%\definecolor{unoffensive-warning}{HTML}{B4DCED}

% This section can be removed at submission.
% ------------------------------------------
\usepackage{color}
\usepackage{datenumber}

\newcounter{dateone}
\newcounter{datetwo}

\newcommand{\difftoday}[3]{%
  \setmydatenumber{dateone}{\the\year}{\the\month}{\the\day}%
  \setmydatenumber{datetwo}{#1}{#2}{#3}%
  \addtocounter{datetwo}{-\thedateone}%
  \the\numexpr(\thedatetwo)\relax\space days}
% ------------------------------------------

@@

\newcommand{\Nspectra}{520,782}
\newcommand{\Nstars}{457,589}
\newcommand{\Nstarsqc}{447,207} % v0.95 finite values
\newcommand{\Nabundances}{1,692,825} %v0.95 finite values

@@

% For AASTeX v6
%\AuthorCallLimit=10
%\fullcollaborationName{The \rave\ Collaboration}

\begin{document}
% Remove at submission:
\slugcomment{{\color{red} \textbf{To appear on arXiv on 13 Sep 2016 (submission in \difftoday{2016}{9}{9})}}}

\title{The \project{unRAVE} catalog}

\author{Andrew R. Casey}
\affil{Institute of Astronomy, Madingley Road, Cambridge CB3 0HA}

% Gilmore, Matijevic, McMillan, Siviero, Wojno

% Specific contributors to this work:
% There is some order already in mind, but final order will be determined by  contribution.
\author{Some combination of: Harry Enke, Kenneth C. Freeman, Gerry Gilmore, Keith Hawkins, David W. Hogg, Sergey Koposov, Georges Kordopatis, Gal Matijevic, Melissa Ness, Jason Sanders, Matthias Steinmetz, Hans Walter-Rix}

% RAVE DR5 core team:
\author{Luca Casagrande, Andrea Kunder, Paul McMillan, Alessandro Siviero, Jennifer Wojno, Toma\v{z} Zwitter}
% Zwitter:  University of Ljubljana, Faculty of Mathematics and Physics, Jadranska 19, 1000 Ljubljana, Slovenia

% RAVE builders
\author{Joss Bland-Hawthorn, Brad K. Gibson, Arnaud Siebert, Olivier Bienayme, Julio F. Navarro, Ulisse Munari, Warren Reid, Rosemary Wyse, Amina Helmi, George Seabroke}
% Bland-Hawthorn: Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia.
% Gibson: E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom.
% Siebert: Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France
% Bienayme: Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France
% Navarro: Senior CIfAR Fellow; Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2
% Munari: INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy
% Reid (1/2): Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia
% Reid (1/2): Western Sydney University, Penrith South DC, NSW 1797
% Wyse: Johns Hopkins University, Baltimore, MD, USA
% Helmi: Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands
% Seabroke: Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, RH5 6NT, UK
\author{and the \rave\ collaboration}

\begin{abstract}
The Milky Way is a powerful laboratory for understanding galaxy formation,
as it can provide orbits, ages, atmospheric parameters, as well as chemical 
abundances for vast sets of individual stars.  These inferences require 
both astrometric and spectroscopic data.  Indeed, in order to be maximally
useful for chemo-dynamic studies, the Tycho-Gaia Astrometric Solution 
(\tgas) sample in the first \gaia\ data release requires a spectroscopic 
complement that includes radial velocities, stellar parameters, and 
elemental abundances.  Among existing spectroscopic samples, the RAdial 
Velocity Experiment (\rave) survey has the largest overlap with \tgas: 
up to 292,036 stars.  We present a data-driven re-analysis of \rave\ 
spectra using \thecannon, and we provide more precise and accurate stellar
parameters and abundances than available in previous \rave\ data releases. 
We constructed our model using high-fidelity \apogee\ stellar parameters 
and abundances for red giant branch stars that overlap with \rave, and 
stellar parameters from the \project{K2}/\project{Ecliptic Pole Input 
Catalog} for main-sequence and sub-giant branch stars.  We derive, and 
validate, improved effective temperature $\teff$, surface gravity $\logg$, 
and chemical abundances of up to seven elements (O, Mg, Al, Si, Ca, Fe, Ni) 
for \Nstarsqc\ stars.  In total we report \Nabundances\ elemental 
abundances, with a typical precision of 0.07~dex.  The \unrave\ catalog 
presented here, in conjunction with \tgas, represents the most powerful 
data set for chemo-orbital analysis at the dawn of broadly available 
\gaia\ data.
\end{abstract}

\keywords{stars: fundamental parameters --- stars: abundances}

@@

The first \gaia\ data release will include the Tycho-Gaia Astrometric Solution
\citep[hereafter \tgas;][]{Michalik_2015a,Michalik_2015b}: positions, proper 
motions, and parallaxes for approximately two million stars in the Tycho-2 
\citep{Hog_2000} catalog.  After cross-matching all major stellar spectroscopic 
surveys\footnote{Specifically we cross-matched the Tycho-2 catalog against the 
\apogee\ \citep{Zasowski_2013}, \ges\ \citep{Gilmore_2012,Randich_2013}, 
\galah\ \citep{DeSilva_2015}, \lamost\ \citep{Cui_2012}, and \rave\ 
\citep{Steinmetz_2006} surveys.}, we found that the RAdial Velocity Experiment 
(\rave) survey is expected to have the largest overlap with the first \gaia\ 
data release: up to 292,036 stars.  We used the \gaia\ universe model snapshot 
\citep{Robin_2012} to estimate the precision in parallax and proper motions that
could be available in the first \gaia\ data release (DR1) for stars in those 
overlap samples.  Comparing the expected precision to what is currently available, 
we further found that the \rave\ survey will benefit most from \gaia\ DR1: the
distances of 63\%of stars in the \rave--\gaia\ DR1 overlap sample 
($\approx$182,862 stars) are expected to improve with the first \gaia\ data release, 
and 47\% of stars ($\approx$137,211 stars) are likely to have better proper motions. 
Although the \gaia\ universe model assumes end-of-mission uncertainties --- and does 
not account for systematics in the first data release --- this calculation still 
provides intuition for the relative improvement that the first \gaia\ data release 
can make to ground-based surveys.  The expected improvements for \rave\ motivated 
us to examine what chemical abundances were available from those data, and to 
evaluate whether we could enable new chemo-dynamic studies by contributing to the
existing set of chemical abundances.

@@

The target selection for \rave\ is based on the $I$-band apparent magnitude,
$9 < I < 12$, with a weak $J - K_s > 0.5$ cut near the disk and bulge \citep{Wojno_2016}.  
The $I$ band was used for the target selection because it has a good overlap with the
wavelength range that \rave\ operates in:  8410--8795~\AA.  The resolution and 
wavelength coverage of \rave\ is comparable to the Radial Velocity Spectrometer on
board the \gaia\ space telescope \citep{Munari_2005,Kordopatis_2011,Recio-Blanco_2016}, 
and the wavelength range overlaps with one of the key setups used for the ground-based 
high-resolution \ges\ survey \citep{Gilmore_2012,Randich_2013}.  The spectral region 
also includes the \ion{Ca}{2} near infrared triplet lines --- strong transitions that 
are dominated by pressure broadening --- which are visible even in metal-poor stars
or spectra with very low signal-to-noise (S/N) ratios.  Atomic transitions of 
light-, $\alpha$-, and Fe-peak elements are present as well, allowing for detailed 
chemical abundance studies.

@@

%\begin{eqnarray}
%\eta_{\logg} & = & \frac{\logg_a - \logg_b}{\sqrt{{\sigma_{\logg,a}}^2 + {\sigma_{\logg,b}}^2}} \quad .
%\end{eqnarray}

@@

As an initial point of comparison, we cross-matched our results against the 
official fourth \rave\ data release (Figure \ref{fig:rave-dr4-comparison}).
In order to provide a fair comparison, we only show stars that meet a number
of quality flags in \emph{both} samples.  Our constraints require that the
S/N ratio exceeds 10~pixel$^{-1}$, and $\chi_r^2 < 3$.  For this comparison
we further required that:
the \texttt{QK} flag from \citet{Kordopatis_2013} is zero, indicating no
problems were reported by the pipeline; $T_{{\rm eff},DR4} > 4000$~K;
the error in radial velocity \texttt{e\_HRV} is $<$8~km~s$^{-1}$; and the three
principal morphological flags \texttt{c1}, \texttt{c2}, \texttt{c3}, from 
\citet{Matijevic_2012} all indicate `n' for a normal FGK-type star.
There is good agreement in $\teff$, with a bias and RMS of just 4~K and 240~K,
respectively. The offset in $\logg$ on the giant branch between this study and 
\citet{Kordopatis_2013} has been noted in other studies (e.g., \apogee), and this issue
has been resolved in the fifth \rave\ data release by correcting $\logg$
values with a calibration sample consisting of asteroseismic targets and the
\gaia\ benchmark stars.  There is also a
slight discrepancy in the $\logg$ values along the main-sequence, where our
work tends to taper down towards higher $\logg$ values at cooler temperatures,
and the \rave\ DR4 sample tends to have a slightly flatter lower main-sequence.
This difference is not likely to have a very significant effect on the detailed
abundance or spectrophotometric distance determinations between these studies 
\citep{Binney_2014}.

@@

We have presented the largest collection of stellar abundances for stars in the 
first \gaia\ data release.  In total we derive reliable stellar atmospheric 
parameters for \Nstarsqc, and report more than 1.69 million abundances.  Despite 
the caveats and limitations discussed here, our validation experiments and 
comparisons with high-resolution spectroscopic studies suggests that our results 
have sufficient accuracy and precision to be useful for chemo-dynamic studies 
that become imminently feasible only in the era of \gaia\ data.  Indeed, we
are optimistic that the \unrave\ catalog will advance understanding of the
Milky Way's formation and evolution.

@@

% TODO: Replace ZENODO-URL with a data url
%\noindent\colorbox{unoffensive-warning}{\parbox{\dimexpr\linewidth-2\fboxsep}{
\noindent{}Source code for this project is available at \texttt{\giturl}\hspace{-0.5em},
and this document was compiled from revision hash \texttt{\githash} in that repository.
Inferred labels, associated errors, and relevant metadata are available electronically
at \texttt{\url{ZENODO-URL}} \citep{ZENODO-CITATION}.  These results are also available
through the \rave\ DR5 database \citep{Kunder_2016}. Please note that it is a condition
of using these results that the fifth \rave\ data release by \citet{Kunder_2016} must 
also be cited, as the work presented here would not have been possible without the 
tireless efforts of the entire \rave\ collaboration, past and present.
%}}

@@

\begin{figure}[p]
\center
\includegraphics[width=0.65\textwidth]{figures/gce.pdf}
\caption{Detailed chemical abundances ([X/Fe]) for giant stars in \unrave\ with respect to [Fe/H], showing the Galactic chemical evolution derived for each element. Note that the y-axis limits vary for each panel, however for clarity we show the scaled-solar position by dashed lines, and have common tick mark spacing on the y-axis for all panels. Only stars meeting our quality constraints are shown (see Section \ref{sec:discussion}).\label{fig:gce}}
\end{figure}

\begin{figure}[p]
\center
\includegraphics[width=0.65\textwidth]{figures/hot-stars.pdf}
\caption{Effective temperatures $\teff$ and surface gravities $\logg$ from this work, where each hexagonal bin is colored by the \emph{maximum} temperature for any star in that bin, as reported by the \rave\ pre-processing pipeline \texttt{SPARV} \citep{Steinmetz_2006,Zwitter_2008}.  Hot stars are not included in our training set, and appear above the turnoff in our labels.  For this reason, we supply a boolean quality control flag \texttt{QC} that flags stars with $\teff > 8000$~K (as reported by \texttt{SPARV}), and other results that are known to be erroneous.\label{fig:hot-stars}}
\end{figure}

>>>>

%% This file is part of the unRAVE Project 
%% Copyright 2016 the authors.  All rights reserved.

\documentclass[preprint]{aastex}

@@

@@

\newcommand{\Nspectra}{520,781}
\newcommand{\Nstars}{457,588}

% TODO: Final checks based on released version.
\newcommand{\Nstarsqc}{447,207} % v0.95 finite values
\newcommand{\Nabundances}{1,692,825} %v0.95 finite values

@@

\begin{document}
\title{The \project{unRAVE} catalog of stellar atmospheric parameters and\\
chemical abundances for chemo-dynamic studies in the \gaia\ era}

\author{Andrew R. Casey\altaffilmark{1}, Keith Hawkins\altaffilmark{1}, David W. Hogg\altaffilmark{2,3,4,5}, Melissa Ness\altaffilmark{5}, Hans Walter-Rix\altaffilmark{5}, Georges Kordopatis\altaffilmark{6}, Andrea Kunder\altaffilmark{6}, Matthias Steinmetz\altaffilmark{6}, Harry Enke\altaffilmark{6}, Jason Sanders\altaffilmark{1}, Sergey Koposov\altaffilmark{1}, Gerry Gilmore\altaffilmark{1}, Toma\v{z} Zwitter\altaffilmark{6}, Kenneth C. Freeman\altaffilmark{7}, Luca Casagrande\altaffilmark{7}, 
Gal Matijevic\altaffilmark{6}, George Seabroke\altaffilmark{8}, Olivier Bienayme\altaffilmark{9}, 
Joss Bland-Hawthorn\altaffilmark{10}, Brad K. Gibson\altaffilmark{11}, Eva~K.~Grebel\altaffilmark{12}, Amina Helmi\altaffilmark{13}, Ulisse Munari\altaffilmark{14}, Julio F. Navarro\altaffilmark{15,16}, Warren Reid\altaffilmark{17,18}, Arnaud Siebert\altaffilmark{19}, Rosemary Wyse\altaffilmark{20}\\
\vspace{2em}
\emph{(Affiliations can be found at the end of the article)}
}

\begin{abstract}
The Milky Way is a powerful laboratory for understanding galaxy formation,
as it can provide orbits, ages, atmospheric parameters, as well as chemical 
abundances for vast sets of individual stars.  These inferences require 
both astrometric and spectroscopic data.  Indeed, in order to be maximally
useful for chemo-dynamic studies, the Tycho-Gaia Astrometric Solution 
(\tgas) sample in the first \gaia\ data release requires a spectroscopic 
complement that includes radial velocities, stellar atmospheric parameters, and 
elemental abundances.  Among existing spectroscopic samples, the RAdial 
Velocity Experiment (\rave) survey has the largest overlap with \tgas: 
$\approx$250,000 stars.  We present a data-driven re-analysis of \rave\ 
spectra using \thecannon, and we provide more precise and accurate stellar
parameters and abundances than available in previous \rave\ data releases. 
We constructed our model using high-fidelity \apogee\ stellar parameters 
and abundances for red giant branch stars that overlap with \rave, and 
stellar parameters from the \project{K2}/\project{Ecliptic Pole Input 
Catalog} for main-sequence and sub-giant branch stars.  We derive, and 
validate, improved effective temperature $\teff$, surface gravity $\logg$, 
and chemical abundances of up to seven elements (O, Mg, Al, Si, Ca, Fe, Ni) 
for \Nstarsqc\ stars.  In total we report \Nabundances\ elemental 
abundances, with a typical precision of 0.07~dex.  The \unrave\ catalog 
presented here, in conjunction with \tgas, represents the most powerful 
data set for chemo-dynamic analysis at the dawn of broadly available 
\gaia\ data.
\end{abstract}

\keywords{stars: fundamental parameters --- stars: abundances
% Clear rest of page
\clearpage}

@@

The first \gaia\ data release will include the Tycho-Gaia Astrometric Solution
\citep[hereafter \tgas;][]{Michalik_2015a,Michalik_2015b}: positions, proper 
motions, and parallaxes for approximately two million stars in the Tycho-2 
\citep{Hog_2000} catalog.  After cross-matching all major stellar spectroscopic 
surveys\footnote{Specifically we cross-matched the Tycho-2 catalog against the 
\apogee\ DR13 \citep{Zasowski_2013}, \ges\ internal DR4 
\citep{Gilmore_2012,Randich_2013}, \galah\ internal DR1 \citep{DeSilva_2015}, 
\lamost\ DR1 \citep{Cui_2012}, and \rave\ DR4 \citep{Steinmetz_2006} catalogs.}, 
we found that the RAdial Velocity Experiment \citep[\rave;][]{Steinmetz_2006} 
survey is expected to have the largest overlap with the first \gaia\ 
% TODO: Sanders: 292,036; Kunder: 264,276
data release: up to 264,276 stars.  We used the \gaia\ universe model snapshot 
\citep{Robin_2012} to estimate the precision in parallax and proper motions that
could be available in the first \gaia\ data release (DR1) for stars in those 
overlap samples.  Comparing the expected precision to what is currently available, 
we further found that the \rave\ survey will benefit most from \gaia\ DR1: the
distances of 63\% of stars in the \rave--\gaia\ DR1 overlap sample are expected 
to improve with the first \gaia\ data release, and 47\% of stars are likely to
have better proper motions.  Although the \gaia\ universe model assumes 
end-of-mission uncertainties --- and does not account for systematics in the 
first data release --- this calculation still provides intuition for the relative
improvement that the first \gaia\ data release can make to ground-based surveys.  
The expected improvements for \rave\ motivated us to examine what chemical 
abundances were available from those data, and to evaluate whether we could 
enable new chemo-dynamic studies by contributing to the existing set of chemical
abundances.

@@

The target selection for \rave\ is based on the $I$-band apparent magnitude,
$9 < I < 12$, with a weak $J - K_s > 0.5$ cut near the disk and bulge \citep{Wojno_2016}.  
The $I$ band was used for the target selection because it has a good overlap with the
wavelength range that \rave\ operates in:  8410--8795~\AA.  The resolution and 
wavelength coverage of \rave\ is comparable to the Radial Velocity Spectrometer on
board the \gaia\ space telescope \citep{Munari_2005,Kordopatis_2011,Recio-Blanco_2016}, 
and the wavelength range overlaps with one of the key setups used for the ground-based 
high-resolution \ges\ survey \citep{Gilmore_2012,Randich_2013}.  The spectral region 
includes the \ion{Ca}{2} near infrared triplet lines --- strong transitions that 
are dominated by pressure broadening --- which are visible even in metal-poor stars
or spectra with very low signal-to-noise (S/N) ratios.  Atomic transitions of 
light-, $\alpha$-, and Fe-peak elements are also present, allowing for detailed 
chemical abundance studies.

@@

@@

As an initial point of comparison, we cross-matched our results against the 
official fourth \rave\ data release (Figure \ref{fig:rave-dr4-comparison}).
In order to provide a fair comparison, we only show stars that meet a number
of quality flags in \emph{both} samples.  Our constraints require that the
S/N ratio exceeds 10~pixel$^{-1}$, and $\chi_r^2 < 3$.  For this comparison
we further required that:
the \texttt{QK} flag from \citet{Kordopatis_2013} is zero, indicating no
problems were reported by the pipeline; $T_{{\rm eff},DR4} > 4000$~K;
the error in radial velocity \texttt{e\_HRV} is $<$8~km~s$^{-1}$; and the three
principal morphological flags \texttt{c1}, \texttt{c2}, \texttt{c3}, from 
\citet{Matijevic_2012} all indicate `n' for a normal FGK-type star.
There is good agreement in $\teff$, with a bias and RMS of just 4~K and 240~K,
respectively. The offset in $\logg$ on the giant branch between this study and 
\citet{Kordopatis_2013} has been noted in other studies (e.g., \apogee), and this issue
has been minimized in the fifth \rave\ data release by correcting $\logg$
values with a calibration sample consisting of asteroseismic targets and the
\gaia\ benchmark stars.  There is also a
slight discrepancy in the $\logg$ values along the main-sequence, where our
work tends to taper down towards higher $\logg$ values at cooler temperatures,
and the \rave\ DR4 sample tends to have a slightly flatter lower main-sequence.
This difference is not likely to have a very significant effect on the detailed
abundance or spectrophotometric distance determinations between these studies 
\citep{Binney_2014}.

@@

We have presented a comprehensive collection of precise stellar abundances 
for stars in the first \gaia\ data release.  In total we derive reliable 
stellar atmospheric parameters for \Nstarsqc, and report more than 1.69 
million abundances.  Despite the caveats and limitations discussed here, 
our validation experiments and comparisons with high-resolution 
spectroscopic studies suggests that our results have sufficient accuracy 
and precision to be useful for chemo-dynamic studies that become imminently 
feasible only in the era of \gaia\ data.  Indeed, we are optimistic that 
the \unrave\ catalog will advance understanding of the Milky Way's 
formation and evolution.

@@

% TODO: Replace ZENODO-URL with a data url
\noindent{}Source code for this project is available at \texttt{\giturl}\hspace{-0.5em},
and this document was compiled from revision hash \texttt{\githash} in that repository.
Inferred labels, associated errors, and relevant metadata are available electronically
at \texttt{\url{ZENODO-URL}} \citep{ZENODO-CITATION}.  These results are also available
through the \rave\ DR5 database \citep{Kunder_2016}. Please note that it is a condition
of using these results that the fifth \rave\ data release by \citet{Kunder_2016} must 
also be cited, as the work presented here would not have been possible without the 
tireless efforts of the entire \rave\ collaboration, past and present.

@@

\begin{figure}[p]
\center
\includegraphics[width=0.65\textwidth]{figures/gce.pdf}
\caption{Detailed chemical abundances ([X/Fe]) for giant stars in \unrave\ with respect to [Fe/H], showing the Galactic chemical evolution derived for each element. Bin densities are scaled logarithmically. Note that the y-axis limits vary for each panel, however for clarity we show the scaled-solar position by dashed lines, and have common tick mark spacing on the y-axis for all panels. Only stars meeting our quality constraints are shown (see Section \ref{sec:discussion}).\label{fig:gce}}
\end{figure}

\begin{figure}[p]
\center
\includegraphics[width=0.65\textwidth]{figures/hot-stars.pdf}
\caption{Effective temperatures $\teff$ and surface gravities $\logg$ from this work, where each hexagonal bin is colored by the \emph{maximum} temperature for any star in that bin, as reported by the \rave\ pre-processing pipeline \texttt{SPARV} \citep{Steinmetz_2006,Zwitter_2008}.  Hot stars are not included in our training set, and appear above the turnoff in our labels.  For this reason, we supply a boolean quality control flag \texttt{QC} that flags stars with $\teff > 8000$~K (as reported by \texttt{SPARV}), and other results that are of poor quality.\label{fig:hot-stars}}
\end{figure}

\altaffiltext{1}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{2}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA}
\altaffiltext{3}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY 10003, USA}
\altaffiltext{4}{Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA}
\altaffiltext{5}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{6}{University of Ljubljana, Faculty of Mathematics and Physics, Jadranska 19, 1000 Ljubljana, Slovenia}
\altaffiltext{7}{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, ACT 2611, Australia}
\altaffiltext{8}{Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, RH5 6NT, UK}
\altaffiltext{9}{Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France}
\altaffiltext{10}{Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia}
\altaffiltext{11}{E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom}
\altaffiltext{12}{Astronomisches Rechen-Institut, Zentrum f\"ur Astronomie der Universit\"at Heidelberg, M\"onchhofstr.\ 12--14, 69120 Heidelberg, Germany}
\altaffiltext{13}{Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands}
\altaffiltext{14}{INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy}
\altaffiltext{15}{Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2}
\altaffiltext{16}{Senior CIfAR Fellow}
\altaffiltext{17}{Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia}
\altaffiltext{18}{Western Sydney University, Penrith South DC, NSW 1797}
\altaffiltext{19}{Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France}
\altaffiltext{20}{Johns Hopkins University, Baltimore, MD, USA}
